---
title: "WMH Actigraphy Correlations"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

## Correlations

```{r setup}
knitr::opts_knit$set(root.dir = normalizePath('/home/WMHactig/data/processed')) 
```

### Load libraries and data

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(correlation)
library(fs)
library(BayesFactor)

# Set directories
base <- '/home/WMHactig'
scripts <- path(base, 'src')
data_raw <- path(base, 'data', 'raw')
data_processed <- path(base, 'data', 'processed')
setwd(data_processed)

df <- read.csv("WMHactig_data.csv")
```

## Correlations
### For correlation table in paper

```{r}
df %>% select(
  # Clinical
  'ATOS_age',
  'ATOS_MMSE',
  'ATOS_GDS15',
  'ATOS_BMI',
  'ATOS_exercise',
  'ATOS_vascular_risk_index',
  # Actig
  'ATOS_Actig_Standard_SE',
  'ATOS_Actig_Standard_Waketime',
  'ATOS_Actig_NonPar_IS',
  'ATOS_Actig_NonPar_IV',
  'ATOS_Actig_NonPar_RA',
  'ATOS_Actig_NonPar_L5',
  'ATOS_Actig_NonPar_M10',
  'ATOS_L5_StartTime_recode'
	) %>%
  correlation(p_adjust = 'none')
```

### Clinical and actigraphy correlations
**NOTE:** No adjustment for multiple comparisons applied and printed correlations only showing those where p <= 0.10.

```{r}
df %>% select(
  # Clinical
  'ATOS_age',
  'ATOS_MMSE',
  'ATOS_GDS15',
  'ATOS_PSQItot',
  'ATOS_BMI',
  'ATOS_exercise',
  'ATOS_vascular_risk_index',
  # Actig
  'ATOS_Actig_NonPar_IS',
  'ATOS_Actig_NonPar_IV',
  'ATOS_Actig_NonPar_RA',
  'ATOS_Actig_NonPar_L5',
  'ATOS_L5_StartTime_recode',
  'ATOS_Actig_NonPar_M10'
	) %>%
  correlation(p_adjust = 'none') %>%
  subset(p <= 0.1, -c(Method, t, df))
```

### Actigraphy and WMH volume correlations
**NOTE:** No adjustment for multiple comparisons applied and printed correlations only showing those where p <= 0.10.

```{r}
df %>% select(
  # Actig
  'ATOS_Actig_NonPar_IS',
  'ATOS_Actig_NonPar_IV',
  'ATOS_Actig_NonPar_RA',
  'ATOS_Actig_NonPar_L5',
  'ATOS_L5_StartTime_recode',
  'ATOS_Actig_NonPar_M10',
  # WMH
  'ATOS_WholeBrainLesion_volume',
  'ATR_left_volume',
  'CST_right_volume',
  'ATR_right_volume',
  'CG_left_volume',
  'CG_right_volume', 
  'CST_left_volume',
  'SLF_I_right_volume',
  'SLF_I_left_volume'
	) %>%
  correlation(p_adjust = 'none') %>%
  subset(p <= 0.1, -c(Method, t, df))
```

### Clinical and WMH volume correlations
**NOTE:** No adjustment for multiple comparisons applied and printed correlations only showing those where p <= 0.10.

```{r}
df %>% select(
  # Clinical
  'ATOS_age',
  'ATOS_MMSE',
  'ATOS_GDS15',
  'ATOS_PSQItot',
  'ATOS_BMI',
  'ATOS_exercise',
  'ATOS_vascular_risk_index',
  # WMH
  'ATOS_WholeBrainLesion_volume',
  'ATR_left_volume',
  'CST_right_volume',
  'ATR_right_volume',
  'CG_left_volume',
  'CG_right_volume', 
  'CST_left_volume',
  'SLF_I_right_volume',
  'SLF_I_left_volume',
	) %>%
  correlation(p_adjust = 'none') %>%
  subset(p <= 0.1, -c(Method, t, df))
```
