---
title: "WML Actigraphy Logistic Models"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

## Description

This document should be used to coordinate model fitting and generation of `.html` summaries defined in the file `logistic_models_base.R`.

### Justification for selection of priors

Weakly informative priors selected for IS, IV, RA, L5 and M10 based on previous literature, and also for BMI in follow-up models due to the well established link between vascular risk factors (such as BMI) with WML.

Non-informative priors selected for L5 start time as previous studies have not included L5 start time and it is unclear *a-priori* whether later or earlier L5 onset would be related to WML volumes. Non-informative priors also chosen for sex as again, there is no clear evidence indicating the sex differences in WML. Non-informative priors also selected for scan-type as this is the first application of MS-GAN on 2D and 3D scans.

Normal priors chosen rather than something with fatter tails (e.g. student's T distribution) as large parameter values are expected to be unlikely.

## Setup

```{r}
library(fs)
library(dplyr)
library(rstanarm)

# Set directories
base <- '/home/WMHactig'
scripts <- path(base, 'src')
data_processed <- path(base, 'data', 'processed')
stats_models <- path(base, 'stats', 'models')
setwd(stats_models)

# Function to render model summaries

render_summary <- function(dv, iv, prior_loc, prior_scale, fname) {
  rmarkdown::render(
  	"logistic_models_base.R", 
  	params = list(
  	  dv = dv,
  	  iv = iv,
  	  prior_loc = prior_loc,
  	  prior_scale = prior_scale
  	  ),
  	output_file = paste0("model_", fname, ".html")
  )
}
```

## Set dependent variables

```{r}
dvs <- c(
  "biATR",
  "biILF",
  "biSLF_II",
  "ATOS_WholeBrainLesion"
)
```

## Fit models

```{r}
for (var in dvs) {
  dv <- paste0(var, "_volume_bin_median")
  prior_scale <- c(1, 1, 2.5, 2.5)
  #####
  # IS
  #####
  iv <- "ATOS_Actig_NonPar_IS_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(-1, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_IS"))
  #####
  # IV
  #####
  iv <- "ATOS_Actig_NonPar_IV_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(1, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_IV"))
  #####
  # RA
  #####
  iv <- "ATOS_Actig_NonPar_RA_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(-1, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_RA"))
  #####
  # L5
  #####
  iv <- "ATOS_Actig_NonPar_L5_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(1, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_L5"))
  #####
  # M10
  #####
  iv <- "ATOS_Actig_NonPar_M10_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(-1, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_M10"))
  #####
  # L5 start time
  #####
  iv <- "ATOS_L5_StartTime_recode_z + ATOS_age_z + ATOS_scan_type + Sex"
  prior_loc <- c(0, 1, 0, 0)
  render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_L5start"))
}
```

## Follow-up models with BMI

```{r}
prior_scale <- c(1, 1, 2.5, 2.5, 1)

#####
# ATR
#####
dv <- "biATR_volume_bin_median"

iv <- "ATOS_Actig_NonPar_IS_z + ATOS_age_z + ATOS_scan_type + Sex + ATOS_BMI_z"
prior_loc <- c(-1, 1, 0, 0, 1)
render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_IS_wBMI"))

iv <- "ATOS_L5_StartTime_recode_z + ATOS_age_z + ATOS_scan_type + Sex + ATOS_BMI_z"
prior_loc <- c(0, 1, 0, 0, 1)
render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_L5start_wBMI"))

#####
# SLF-II
#####
dv <- "biSLF_II_volume_bin_median"

iv <- "ATOS_L5_StartTime_recode_z + ATOS_age_z + ATOS_scan_type + Sex + ATOS_BMI_z"
prior_loc <- c(0, 1, 0, 0, 1)
render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_L5start_wBMI"))

#####
# Whole Brain
#####
dv <- "ATOS_WholeBrainLesion_volume_bin_median"

iv <- "ATOS_Actig_NonPar_IS_z + ATOS_age_z + ATOS_scan_type + Sex + ATOS_BMI_z"
prior_loc <- c(-1, 1, 0, 0, 1)
render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_IS_wBMI"))

iv <- "ATOS_Actig_NonPar_L5_z + ATOS_age_z + ATOS_scan_type + Sex + ATOS_BMI_z"
prior_loc <- c(1, 1, 0, 0, 1)
render_summary(dv, iv, prior_loc, prior_scale, paste0(var, "_L5_wBMI"))
```

